\sout{Machine Learning for Global Conquest} \\ Multimatrices and Their Derivatives

### 2020-08-16 Math/book.tex
Doing some scratch work.

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\shape}[1]{\left|#1\right|}

@@

Multimatrix identities also have the nice property of being communicative when multiplied
across multiples of their base shape and completely engulfing a smaller multimatrix.

\begin{theorem}[Communicativity of Multiplicative Identities]
Let $X$ be a multimatrix of shape $k * \vec{x}$ where $k$ is some natural number.
Remember (from the identity definition) that the $*$ operator denote successive concatenations of a vector so that,
\[ k * \vec{x} = \bigoplus_{i=1}^k \vec{x} \]
Then for any $n \ge k$,
\[ X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \]
\end{theorem}
\begin{proof}
Given that $\shape{X} = k * \vec{x}$ we know that
$\shape{X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x})} = (n-k) * \vec{x}$.
Let $\bar{x}_1, \bar{x}_2 \ldots \bar{x}_{n-k}$ each be index vectors in $\Dim(\vec{x})$,
for simplicity denoted as,
\[ \bar{x}_I = \bigoplus_{i=1}^{n-k} \bar{x}_i \]
We'll also need a similarly denoted $\bar{y}_1 \ldots \bar{y}_k$ for the free indicies of
the sum below and that shall also be represented as,
\[ \bar{y}_J = \bigoplus_{j=1}^{k} \bar{y}_j \]
Then we know that,
\[
  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
  = \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I]
\]
Notice that $\Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] = \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J]$
since the sub index vectors will always either be equal or not equal, $1$ or $0$, their order doesnt matter.
So,
\begin{align*}
  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
  &= \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] \\
  &= \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] X[\bar{y}_J] \\
  &= \left(\Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \right)[\bar{x}_I]
\end{align*}
\end{proof}

@@

@@

\begin{theorem}[Hadamard Multiplication Rule]
Let $F(X)$ and $G(X)$ be functions of $X$ where
$\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$
then,
\[
  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
\]
\end{theorem}
\begin{landscape}
\begin{proof}
For $\vec{x} = \shape{X}$ and for $\bar{a} \in \Dim(\vec{a})$ etc,
\begin{align*}
\frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
  &= \frac{\partial (F(X) \dmult{\shape{\vec{c}}} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
  &= \frac{\partial (F(X)[\bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{a}])}{\partial X[\bar{x}]} \\
  &= \frac{\partial F(X)[\bar{a} \oplus \bar{c}]}{\partial X[\bar{x}]} G(X)[\bar{c} \oplus \bar{b}]
    + F(X)[\bar{a} \oplus \bar{c}] \frac{\partial G(X)[\bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
    + F(X)[\bar{a} \oplus \bar{c}] \frac{dG}{dX}[\bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left\{ F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}
    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
\end{align*}
\end{proof}
\end{landscape}

@@

\begin{landscape}
\begin{theorem}[Derivative of FFNN Layer]
\[
  \frac{dL_i}{dW_j}
	= \left\{
  \begin{array}{ll}
		0 & \mbox{if } i < j \\
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
	  & \mbox{if } i = j \\
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \Tran(W_i, \shape{\shape{L_{i-1}}})
    \mmult{\shape{\shape{L_{i-1}}}}
    \frac{d L_{i-1}}{dW_j}
		& \mbox{if } i > j
  \end{array}
  \right.
\]
\end{theorem}
\begin{proof}
\begin{ppart} When $i < j$,
$L_i$ does not depend on $W_j$, so 
$\forall \bar{x} \in \Dim(\shape{L_i}), \bar{y} \in \Dim(\shape{W_j})$
$\frac{dL_i}{dW_j} = 0$
\end{ppart}
\begin{ppart} $i = j$
Then note that $\frac{dL_{i-1}}{dW_j} = 0$ because $L_{i-1}$ does not
depend on $W_j$. So we can just use the chain rule and the right multiplicative rule to find that,
\[
  \frac{dL_i}{dW_{j=i}} =
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
\]
\end{ppart}
\begin{ppart} $i > j$
In this case, $L_{i-1}$ depends on $W_j$ but $W_i$ does not. So we can use the chain rule and the
left multiplicative rule to find that,
\begin{align*}
  \frac{dL_i}{dW_{j<i}}
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dW_j} \\
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(
      \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dL_{i-1}}
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{dL_{i-1}}{dW_j}
    \right) \\
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(
      \left(
        \Ident^2(\shape{L_{i}})
        \mmult{\shape{\shape{W_i}}-\shape{\shape{L_{i-1}}}}
        \Tran(W_i, \shape{\shape{L_{i-1}}})
      \right)
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \right) \\
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(
      \left(
        \Ident^2(\shape{L_{i}})
        \mmult{\shape{\shape{L_i}}}
        \Tran(W_i, \shape{\shape{L_{i-1}}})
      \right)
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \right) \\
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(
      \Tran(W_i, \shape{\shape{L_{i-1}}})
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \right) \\
  &=
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \Tran(W_i, \shape{\shape{L_{i-1}}})
    \mmult{\shape{\shape{L_{i-1}}}}
    \frac{d L_{i-1}}{dW_j}
\end{align*}
\end{ppart}
\end{proof}
\end{landscape}

@@

>>>>

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\Part}{Part}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
\newcommand{\shape}[1]{\left|#1\right|}

@@

Multimatrix identities also have the nice property of being commutative when multiplied
across multiples of their base shape and completely engulfing a smaller multimatrix.

\begin{theorem}[Commutativity of Multiplicative Identities]
\label{ident_commute}
Let $X$ be a multimatrix of shape $k * \vec{x}$ where $k$ is some natural number.
Remember (from the identity definition) that the $*$ operator denote successive concatenations of a vector so that,
\[ k * \vec{x} = \bigoplus_{i=1}^k \vec{x} \]
Then for any $n \ge k$,
\[ X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \]
\end{theorem}
\begin{proof}
Given that $\shape{X} = k * \vec{x}$ we know that
$\shape{X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x})} = (n-k) * \vec{x}$.
Let $\bar{x}_1, \bar{x}_2 \ldots \bar{x}_{n-k}$ each be index vectors in $\Dim(\vec{x})$,
for simplicity denoted as,
\[ \bar{x}_I = \bigoplus_{i=1}^{n-k} \bar{x}_i \]
We'll also need a similarly denoted $\bar{y}_1 \ldots \bar{y}_k$ for the free indicies of
the sum below and that shall also be represented as,
\[ \bar{y}_J = \bigoplus_{j=1}^{k} \bar{y}_j \]
Then we know that,
\[
  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
  = \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I]
\]
Notice that $\Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] = \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J]$
since the sub index vectors will always either be equal or not equal, $1$ or $0$, their order doesnt matter.
So,
\begin{align*}
  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
  &= \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] \\
  &= \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] X[\bar{y}_J] \\
  &= \left(\Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \right)[\bar{x}_I]
\end{align*}
\end{proof}

@@

\begin{theorem}[Cubic Identity Multiplication]
\label{hada_cubic}
If $A$ and $B$ are multimatrixes of shaep, $\shape{A} = \vec{a} \oplus \vec{x}$
and $\shape{B} = \vec{x} \oplus \vec{b}$ respectively. Then,
\[ A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B = A \dmult{\shape{\vec{x}}} B \]
\end{theorem}
\begin{proof}
\[ \shape{A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B} = \vec{a} \oplus \vec{x} \oplus \vec{b}  \]
For all $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and $\bar{x} \in \Dim(\vec{x})$, 
\begin{align*}
  (A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B)[\bar{a} \oplus \bar{x} \oplus \bar{b}]
  &= \sum_{\forall \bar{x}_1, \bar{x_2}} A[\bar{a} \oplus \bar{x}_1] \Ident^3(\vec{x})[\bar{x}_1 \oplus \bar{x} \oplus \bar{x}_2] B[\bar{x}_2 \oplus \bar{b}] \\
  &= A[\bar{a} \oplus \bar{x}] \Ident^3(\vec{x})[\bar{x} \oplus \bar{x} \oplus \bar{x}] B[\bar{x} \oplus \bar{b}] \\
  &= A[\bar{a} \oplus \bar{x}] B[\bar{x} \oplus \bar{b}] \\
  &= (A \dmult{\shape{\vec{x}}} B) [\bar{a} \oplus \bar{x} \oplus \bar{b}]
\end{align*}
\end{proof}

@@

\begin{theorem}[Hadamard Multiplication Rule]
\label{hadamard_rule}
Let $F(X)$ and $G(X)$ be functions of $X$ where
$\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$
then,
\[
  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
\]
\end{theorem}
\begin{landscape}
\begin{proof}
For $\vec{x} = \shape{X}$ and for $\bar{a} \in \Dim(\vec{a})$ etc,
\begin{align*}
\frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
  &= \frac{\partial (F(X) \dmult{\shape{\vec{c}}} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
  &= \frac{\partial (F(X)[\bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{a}])}{\partial X[\bar{x}]} \\
  &= \frac{\partial F(X)[\bar{a} \oplus \bar{c}]}{\partial X[\bar{x}]} G(X)[\bar{c} \oplus \bar{b}]
    + F(X)[\bar{a} \oplus \bar{c}] \frac{\partial G(X)[\bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
    + F(X)[\bar{a} \oplus \bar{c}] \frac{dG}{dX}[\bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
  &= \left\{ F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}
    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
\end{align*}
\end{proof}
\end{landscape}

@@

\begin{theorem}[Derivative of FFNN Layer]
  \frac{dL_i}{dW_j}
	= \left\{
		0 & \mbox{if } i < j \\
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
	  & \mbox{if } i = j \\
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \Tran(W_i, \shape{\shape{L_{i-1}}})
    \mmult{\shape{\shape{L_{i-1}}}}
    \frac{d L_{i-1}}{dW_j}
		& \mbox{if } i > j
  \right.
\begin{ppart} When $i < j$,
$L_i$ does not depend on $W_j$, so 
$\forall \bar{x} \in \Dim(\shape{L_i}), \bar{y} \in \Dim(\shape{W_j})$
$\frac{dL_i}{dW_j} = 0$
\end{ppart}
\begin{ppart} $i = j$
Then note that $\frac{dL_{i-1}}{dW_j} = 0$ because $L_{i-1}$ does not
depend on $W_j$. So we can just use the chain rule and the right multiplicative rule to find that,
  \frac{dL_i}{dW_{j=i}} =
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
Now will a little manipulation, keeping in mind how identies are sometimes commutative (Thm. \ref{ident_commute})
and how cubic identities collapse into hadamard products (Thm. \ref{hada_cubic}),
  \frac{dL_i}{dW_{j=i}}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)\right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
    \left(a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \mmult{\shape{\shape{L_i}}} \Ident^3(\shape{L_i})\right) 
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \mmult{\shape{\shape{L_i}}} \Ident^3(\shape{L_i})
    \mmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \dmult{\shape{\shape{L_i}}}
    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
\end{ppart}
\begin{ppart} $i > j$
In this case, $L_{i-1}$ depends on $W_j$ but $W_i$ does not. So we can use the chain rule and the
left multiplicative rule to find that,
  \frac{dL_i}{dW_{j<i}}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dW_j} \\
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
      \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dL_{i-1}}
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{dL_{i-1}}{dW_j}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
        \Ident^2(\shape{L_{i}})
        \mmult{\shape{\shape{W_i}}-\shape{\shape{L_{i-1}}}}
        \Tran(W_i, \shape{\shape{L_{i-1}}})
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
        \Ident^2(\shape{L_{i}})
        \mmult{\shape{\shape{L_i}}}
        \Tran(W_i, \shape{\shape{L_{i-1}}})
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
      \Tran(W_i, \shape{\shape{L_{i-1}}})
      \mmult{\shape{\shape{L_{i-1}}}}
      \frac{d L_{i-1}}{dW_j}
    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
    \mmult{\shape{\shape{L_i}}}
    \Tran(W_i, \shape{\shape{L_{i-1}}})
    \mmult{\shape{\shape{L_{i-1}}}}
    \frac{d L_{i-1}}{dW_j}
\end{ppart}

@@

\begin{definition}[Multimatrix Concatenation]
Let $A$ and $B$ be multimatricies of shape $\shape{A} = \vec{a}$ and
$\shape{B} = \vec{b}$ respectively. Then if, for all $i \ne n$,
$\vec{a}[i] = \vec{b}[i]$, the following operation is valid,
\[ A \mconcat{n} B \]
In layman's terms, this is the operation of stacking two similar multimatricies on top of or to the side of one another.
It's just complicated by this being an opperation in multiple dimensions.
Formally we'll say that, 
\[ \shape{\shape{A \mconcat{n} B}} = \shape{\shape{A}} = \shape{\shape{B}} \]
\[
  \shape{A \mconcat{n} B}[i] = \left\{
  \begin{array}{ll}
	  \vec{a}[i] + \vec{b}[i] & \mbox{if } i = n \\
	  \vec{a}[i] & \mbox{if } i \ne n
  \end{array}
 \right.
\]
And for all sub index metricies $\bar{l}$ and $\bar{r}$ of lengths $\shape{\bar{l}} = n-1$ and $\shape{\bar{r}} = \shape{\shape{A}}-n$ respectively,
and natural number $j \in [1,\vec{a}[n]+\vec{b}[n]]$ such that $\bar{l} \oplus \left<j\right> \oplus \bar{r} \in \Dim(\shape{A \mconcat{n} B})$,
\[
  \left(A \mconcat{n} B\right)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = \left\{
  \begin{array}{ll}
	  A[\bar{l} \oplus \left<j\right> \oplus \bar{r}] & \mbox{if } j  \le \vec{a}[n] \\
	  A[\bar{l} \oplus \left<j-\vec{a}[n]\right> \oplus \bar{r}] & \mbox{if } j > \vec{a}[n]
  \end{array}
 \right.
\]
\end{definition}

\begin{definition}[Multimatrix Partitions]
Let $M$ be some multimatrix of shape $\vec{m}$.
Then for any natural number $n \in [1, \shape{\vec{m}}]$, the dimension,
and natural number $k \in [1,\vec{m}[n]-1]$, the split,
\[ \Part(M, n, k) = \{M_1, M_2\} \]
\[ \Part_1(M, n, k) = M_1 \]
\[ \Part_2(M, n, k) = M_2 \]
Where $M_1 \mconcat{n} M_2 = M$ and $\shape{M_1}[n] = k$ (therefore $\shape{M_2}[n] = \vec{m}[n]-k$).

In essence, this is the inverse operation of multimatrix concatenation.

Let $\vec{l}$ and $\vec{r}$ be vectors of length $n-1$ and $\shape{\vec{m}}-n$ respectively
such that $\vec{l} \oplus \left<\vec{m}[n]\right> \oplus \vec{r} = \vec{m}$ then
\[ \shape{\Part_1(M, n, k)} = \vec{l} \oplus \left<k\right> \oplus \vec{r} \]
\[ \shape{\Part_2(M, n, k)} = \vec{l} \oplus \left<\vec{m}[n]-k\right> \oplus \vec{r} \]

For all $\bar{l} \in \Dim(\vec{l})$, $\bar{r} \in \Dim(\vec{r})$, and $j \in [1, k]$,
\[ \Part_1(M, n, k)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = M[\bar{l} \oplus \left<j\right> \oplus \bar{r}] \]

And for all $\bar{l} \in \Dim(\vec{l})$, $\bar{r} \in \Dim(\vec{r})$, and $j \in [1, \vec{m}[n]-k]$,
\[ \Part_2(M, n, k)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = M[\bar{l} \oplus \left<j+k\right> \oplus \bar{r}] \]
\end{definition}

\begin{theorem}[Multiplication Over Concatenation Rules]
Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid.

For any natural number $m$ where $m < n$,
if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid then,
\[ C \mmult{m} \left(A \mconcat{n} B\right) = \left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right) \]

And if $m \le \shape{\shape{A}}-n$
then if and only if  $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid then,
\[ \left(A \mconcat{n} B\right) \mmult{m} C = \left(A \mmult{m} C\right) \mconcat{n} \left(B \mmult{m} C\right) \]

And when $m \ge n$, if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid,
then for the multimatrices $C_1$ and $C_2$ defined by,
\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \{C_1, C_2\} \]
\[
  C \mmult{m} \left(A \mconcat{n} B\right)
  =
  \left( C_1 \mmult{m} A \right) + 
  \left( C_1 \mmult{m} B \right)
\]
